---
title: "Pre-analyis"
author: "Siwei Wu"
date: "2023/3/8"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


It's a pre-analysis script for lasso regression. Copy the codes in this script to the start of your script for analysis.
(1) We choose variables which will be used for lasso, and get rid of the unnecessary ones, like sex and data of enrollment.
(2) We transform all categorical variables into ordinal variables(integer):
  2.1 For variables with only two levels, they are encoded as 0 or 1
  2.2 For variables with more than 2 levels, they are encoded as 1, 2, 3, and so on 
You may need to do some changes if you are going to run other models. For instance, when running univariate logistic, you still keep binary variables to be factor.



```{r}
# set up working directory
rm(list=ls())
path <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(path)

# load packages
library(tidyverse)
library(dplyr)
library(RColorBrewer)
library(mice)
library(OpenMx)
library(igraph)
library(sharp)
library(fake)
rm(path)

# Read in dataset 
ukb = readRDS("ukb_0501.rds")
```


# Pre-analysis
## Transform factors to ordinal variables
```{r}
# Re-code Sleep_snoring.0.0 and Female_Ever_use_HRT.0.0 (binary variables)
ukb$Sleep_snoring.0.0 = ifelse(ukb$Sleep_snoring.0.0=="No", 0, 1)
ukb$Female_Ever_use_HRT.0.0 = ifelse(ukb$Female_Ever_use_HRT.0.0=="No", 0, 1)

# Select factor variables
ukb_cate= ukb %>% select(eid, is.factor)

# Transform factors into ordinal variables
ukb_ordinal = as.data.frame(lapply(ukb_cate, as.numeric))
  
# Select non factor variables
ukb_nonfactor = ukb %>% select(-is.factor)
ukb_nonfactor$eid = as.numeric(ukb$eid)

# Merge
ukb = inner_join(ukb_ordinal, ukb_nonfactor)

rm(ukb_cate, ukb_ordinal, ukb_nonfactor)
```

## factor binary variables(only for univariate analysis)
```{r}
## factor binary variables(only for univariate variables)
# ukb$Sleep_snoring.0.0 = factor(ukb$Sleep_snoring.0.0)
# ukb$Mother_breast_cancer = factor(ukb$Mother_breast_cancer)
# ukb$Mother_cancer = factor(ukb$Mother_cancer)
# ukb$Mother_breast_cancer = factor(ukb$Mother_breast_cancer)
# ukb$Mother_cancer = factor(ukb$Mother_cancer)
# ukb$Female_Menopause_no = factor(ukb$Female_Menopause_no )
# ukb$Female_Menopause_unsure = factor(ukb$Female_Menopause_unsure)
# ukb$Female_Menopause_yes = factor(ukb$Female_Menopause_yes)
# ukb$Female_Ever_use_HRT.0.0 = factor(ukb$Female_Ever_use_HRT.0.0)
# rm(ukb_cate, ukb_ordinal, ukb_nonfactor)
```

## Transform logical variables into numeric
```{r}
ukb$Mother_breast_cancer = as.numeric(ukb$Mother_breast_cancer)
```

## Pick up variables necessary for analysis and reorder the variables
```{r}
rownames(ukb) = ukb$eid
ukb = ukb %>% select(-eid)

# Re-arrange the  variables
## Biochemical metrics
sex_horm = c("Bio_shbg.0.0","Bio_testosterone.0.0")
glucose = c("Bio_glucose.0.0", "Bio_glycated_haemoglobin.0.0", "Bio_igf_1.0.0")
liver = c("Bio_alkaline_phosphate.0.0", "Bio_alanine_aminotransferase.0.0", "Bio_aspartate_aminotransferase.0.0", "Bio_direct_bilirubin.0.0", "Bio_gamma_glutamyltransferase.0.0", "Bio_total_bilirubin.0.0")
lipid = c("Bio_apolipoprotein_a.0.0", "Bio_apolipoprotein_b.0.0", "Bio_cholesterol.0.0", "Bio_hdl_cholesterol.0.0", "Bio_ldl_direct.0.0", "Bio_lipoprotein_a.0.0", "Bio_triglycerides.0.0")
nutrit = c("Bio_albumin.0.0", "Bio_total_protein.0.0")
inflam = c("Bio_c_reac_protein.0.0")
urate = c("Bio_urate.0.0")
skeleton = c("Bio_calcium.0.0", "Bio_phosphate.0.0", "Bio_vitamin_d.0.0")
kidney = c("Bio_urea.0.0", "Bio_creatinine.0.0", "Bio_cystatin_c.0.0")

## Physical Measurement, environment, and demographic variables
# PhyMeas = c("phyMeas_SBP", "phyMeas_DBP", "PhyMeas_waist_cir.0.0", "PhyMeas_BMI.0.0")
PhyMeas = c("PhyMeas_BMI.0.0", "phyMeas_SBP", "phyMeas_DBP")
demo = c("Age_enrollment.0.0", "income_household.0.0", "Education","Employment_no_or_cnt_wk","Employment_paid_or_sf_emply","Employment_unpaid_wk_or_funded")
PhyAC = c("Days_WK_PhyAc.0.0")
envir = c("no2_air_pol.0.0","no_air_pol.0.0")

ukb = ukb %>% select(
  all_of(demo), 
  starts_with("Female_"), 
  starts_with("Mother_"), 
  envir, 
  PhyAC,
  starts_with("Sleep_"), 
  starts_with("Smoke_"), 
  starts_with("Alcohol_"), 
  starts_with("Diet_"), 
  all_of(PhyMeas),
  all_of(sex_horm), 
  all_of(glucose), 
  all_of(liver), 
  all_of(lipid), 
  all_of(nutrit), 
  all_of(inflam), 
  all_of(urate), 
  all_of(skeleton), 
  all_of(kidney), 
  starts_with("Urine_"),
  breast_incident_case,
  uterus_incident_case, 
  ovary_incident_case, 
  # others_incident_case, 
  femalecancer_incident_case)

rm(PhyMeas, demo, envir, sex_horm, glucose, liver, lipid, nutrit, inflam, urate, skeleton, kidney)

```

Binary variabels
```{r}
# To decide whether scale binary variables or not: the following are binary variables 
# Binary_variable = c("Employment_no_or_cnt_wk", "Employment_paid_or_sf_emply", "Employment_unpaid_wk_or_funded", "Female_Ever_use_HRT.0.0", "Female_Menopause_no", "Female_Menopause_unsure", "Female_Menopause_yes", "Mother_breast_cancer")
```

Create data set for each cancer
```{r}
# Female cancer
ukb_female = ukb %>% select(-ovary_incident_case, -uterus_incident_case, -breast_incident_case)
# ukb_female = ukb %>% select(-ovary_incident_case, -uterus_incident_case, -others_incident_case, -breast_incident_case)

# Factor Outcome
ukb_female$femalecancer_incident_case = factor(ukb_female$femalecancer_incident_case)

# Split X and Y
ukb_female_x = as.matrix(ukb_female %>% select(-femalecancer_incident_case))
ukb_female_x = scale(ukb_female_x)
ukb_female_y = as.matrix(ukb_female %>% select(femalecancer_incident_case))
```

```{r}
# Breast cancer
# ukb_breast = ukb %>% filter(uterus_incident_case == 0 | breast_incident_case==1) %>% 
#   filter(ovary_incident_case == 0 | breast_incident_case==1) %>% 
#   filter(others_incident_case == 0| breast_incident_case==1) %>% 
#   select(-ovary_incident_case, -uterus_incident_case, -others_incident_case,-femalecancer_incident_case)
ukb_breast = ukb %>% filter(uterus_incident_case == 0 | breast_incident_case==1) %>% 
  filter(ovary_incident_case == 0 | breast_incident_case==1) %>% 
  select(-ovary_incident_case, -uterus_incident_case,-femalecancer_incident_case)

# Factor Outcome
ukb_breast$breast_incident_case = factor(ukb_breast$breast_incident_case)

# Split X and Y
ukb_breast_x = as.matrix(ukb_breast %>% select(-breast_incident_case))
ukb_breast_x = scale(ukb_breast_x)
ukb_breast_y = as.matrix(ukb_breast %>% select(breast_incident_case))

```

```{r}
# Ovary cancer
# ukb_ovary = ukb %>% filter(uterus_incident_case == 0 | ovary_incident_case == 1 ) %>%
#   filter(breast_incident_case == 0 | ovary_incident_case == 1 ) %>%
#   filter(others_incident_case == 0 | ovary_incident_case == 1 ) %>%
#   select(-breast_incident_case, -uterus_incident_case, -others_incident_case,-femalecancer_incident_case)
ukb_ovary = ukb %>% filter(uterus_incident_case == 0 | ovary_incident_case == 1 ) %>%
  filter(breast_incident_case == 0 | ovary_incident_case == 1 ) %>%
  select(-breast_incident_case, -uterus_incident_case,-femalecancer_incident_case)

# Factor Outcome
ukb_ovary$ovary_incident_case = factor(ukb_ovary$ovary_incident_case)

# Split X and Y
ukb_ovary_x = as.matrix(ukb_ovary %>% select(-ovary_incident_case))
ukb_ovary_x = scale(ukb_ovary_x)
ukb_ovary_y = as.matrix(ukb_ovary %>% select(ovary_incident_case))
```

```{r}
# Uterus cancer
# ukb_uterus = ukb %>% filter(breast_incident_case == 0 | uterus_incident_case==1) %>% filter(ovary_incident_case == 0| uterus_incident_case==1) %>% filter(others_incident_case == 0| uterus_incident_case==1) %>% select(-ovary_incident_case, -breast_incident_case, -others_incident_case,-femalecancer_incident_case)
ukb_uterus = ukb %>% filter(breast_incident_case == 0 | uterus_incident_case==1) %>% 
  filter(ovary_incident_case == 0| uterus_incident_case==1) %>% 
  select(-ovary_incident_case, -breast_incident_case,-femalecancer_incident_case)
# Factor Outcome
ukb_uterus$uterus_incident_case = factor(ukb_uterus$uterus_incident_case)

# Split X and Y
ukb_uterus_x = as.matrix(ukb_uterus %>% select(-uterus_incident_case))
ukb_uterus_x = scale(ukb_uterus_x)
ukb_uterus_y = as.matrix(ukb_uterus %>% select(uterus_incident_case))
```
