---
title: "TDS_Female cancers"
author: "Siwei Wu"
date: "2023/2/10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Pre-analysis
set working directory and load packages
```{r}
# set up working directory
# rm(list=ls())
path <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(path)

# load packages
library(tidyverse)
library(dplyr)
library(RColorBrewer)
rm(path)

# Read in dataset 
ukb = readRDS("ukb_varsel_0501.rds")
```

## Data preparation
Transform factors to ordinal variables
```{r}
# Re-code Sleep_snoring.0.0 and Female_Ever_use_HRT.0.0 (binary variables)
ukb$Sleep_snoring.0.0 = ifelse(ukb$Sleep_snoring.0.0=="No", 0, 1)
ukb$Female_Ever_use_HRT.0.0 = ifelse(ukb$Female_Ever_use_HRT.0.0=="No", 0, 1)

# Select factor variables
ukb_cate= ukb %>% select(eid, is.factor)

# Transform factors into ordinal variables
ukb_ordinal = as.data.frame(lapply(ukb_cate, as.numeric))
ukb_ordinal
  
# Select non factor variables
ukb_nonfactor = ukb %>% select(-is.factor)
ukb_nonfactor$eid = as.numeric(ukb$eid)

# Merge
ukb = inner_join(ukb_ordinal, ukb_nonfactor)
```

```{r}
## factor binary variables(only for uni-variate variables)
ukb$Sleep_snoring.0.0 = factor(ukb$Sleep_snoring.0.0)
ukb$Mother_breast_cancer = factor(ukb$Mother_breast_cancer)
ukb$Female_Menopause_no = factor(ukb$Female_Menopause_no )
ukb$Female_Menopause_unsure = factor(ukb$Female_Menopause_unsure)
ukb$Female_Menopause_yes = factor(ukb$Female_Menopause_yes)
ukb$Female_Ever_use_HRT.0.0 = factor(ukb$Female_Ever_use_HRT.0.0)
ukb$Employment_no_or_cnt_wk = factor(ukb$Employment_no_or_cnt_wk)
ukb$Employment_unpaid_wk_or_funded = factor(ukb$Employment_unpaid_wk_or_funded)
ukb$Employment_paid_or_sf_emply = factor(ukb$Employment_paid_or_sf_emply )
rm(ukb_cate, ukb_ordinal, ukb_nonfactor)
```

Data preparation
```{r}
rownames(ukb) = ukb$eid
ukb = ukb %>% select(-eid)

# Re-arrange the  variables
## Biochemical metrics
sex_horm = c("Bio_shbg.0.0","Bio_testosterone.0.0")
glucose = c("Bio_glucose.0.0", "Bio_glycated_haemoglobin.0.0", "Bio_igf_1.0.0")
liver = c("Bio_alkaline_phosphate.0.0", "Bio_alanine_aminotransferase.0.0", "Bio_aspartate_aminotransferase.0.0", "Bio_direct_bilirubin.0.0", "Bio_gamma_glutamyltransferase.0.0", "Bio_total_bilirubin.0.0")
lipid = c("Bio_apolipoprotein_a.0.0", "Bio_apolipoprotein_b.0.0", "Bio_cholesterol.0.0", "Bio_hdl_cholesterol.0.0", "Bio_ldl_direct.0.0", "Bio_lipoprotein_a.0.0", "Bio_triglycerides.0.0")
nutrit = c("Bio_albumin.0.0", "Bio_total_protein.0.0")
inflam = c("Bio_c_reac_protein.0.0")
urate = c("Bio_urate.0.0")
skeleton = c("Bio_calcium.0.0", "Bio_phosphate.0.0", "Bio_vitamin_d.0.0")
kidney = c("Bio_urea.0.0", "Bio_creatinine.0.0", "Bio_cystatin_c.0.0")

## Physical Measurement, environment, and demographic variables
# PhyMeas = c("phyMeas_SBP", "phyMeas_DBP", "PhyMeas_waist_cir.0.0", "PhyMeas_BMI.0.0")
PhyMeas = c("PhyMeas_BMI.0.0", "phyMeas_SBP", "phyMeas_DBP")
demo = c("Age_enrollment.0.0", "income_household.0.0", "Education","Employment_no_or_cnt_wk","Employment_paid_or_sf_emply","Employment_unpaid_wk_or_funded")
PhyAC = c("Days_WK_PhyAc.0.0")
envir = c("no2_air_pol.0.0","no_air_pol.0.0")

ukb = ukb %>% select(
  all_of(demo), 
  starts_with("Female_"), 
  starts_with("Mother_"), 
  envir, 
  PhyAC,
  starts_with("Sleep_"), 
  starts_with("Smoke_"), 
  starts_with("Alcohol_"), 
  starts_with("Diet_"), 
  all_of(PhyMeas),
  all_of(sex_horm), 
  all_of(glucose), 
  all_of(liver), 
  all_of(lipid), 
  all_of(nutrit), 
  all_of(inflam), 
  all_of(urate), 
  all_of(skeleton), 
  all_of(kidney), 
  starts_with("Urine_"),
  breast_incident_case,
  uterus_incident_case, 
  ovary_incident_case, 
  # others_incident_case, 
  femalecancer_incident_case)

rm(PhyMeas, demo, envir, sex_horm, glucose, liver, lipid, nutrit, inflam, urate, skeleton, kidney)
```


# Univariate analysis
## Preparation for analysis: function for uni-variate analysis
```{r}
# df is a data.frame with 2:k-1 columns as exposures, column 1 as the age of enrollment to be adjusted, and column k as the outcome (femalecancer_incident_case)
# logit_df is the data.frame for Manhattan plot you can leave it as default if you don't need to plot different groups of exposures on the same Manhattan plot 
uni_var_anly = function(df, logit_df = matrix(NA,0,4)){
  colnames(logit_df) = c("Estimate", "P value", "2.5%", "97.5%")
  df_varname = colnames(df[,2:(dim(df)[2]-1)])
  df_varname = sub('.0.0', '', df_varname)
  df_varname = gsub('_', ' ', df_varname)
  # Perform uni-variate analysis
  for(i in 2:(dim(df)[2]-1)){
    logit = glm(df[,dim(df)[2]] ~ Age_enrollment.0.0 + df[,i], df, family = binomial)
    logit_result = cbind(summary(logit)$coefficient[-1:-2, 1], max(summary(logit)$coefficient[-1:-2, 4],2e-16), confint.default(logit)[-1:-2,1], confint.default(logit)[-1:-2,2])
    row.names(logit_result) = paste0(df_varname[i-1])
    # row.names(logit_result) = paste0(df_varname[i-1],": ", levels(df[,i])[-1])
    #, " vs ", levels(df[,i])[1])
    logit_df = rbind(logit_df, logit_result)
  }
  return(logit_df)
}
```

## Preparation for analysis: function for manhattan_plot(bonferroni) (one subtype)
```{r}
# logit_df as the output of uni-variate analysis function 
# main as the title of your Manhattan_plot
manhattan_plot_BF = function(logit_df, main){
  MyPal = brewer.pal("Paired", n = 12)
  par(mar=c(7, 0.5, 2, 0.5))
  plot(-log10(logit_df[, 2]), pch = 20, col = ifelse(logit_df[, 1] < 0, yes = MyPal[2], no = MyPal[8]), xaxt = "n", ylab = expression(-log[10](italic(p))), xlab = "", las = 1, ylim = c(min(c(-log10(logit_df[,2]))), max(c(-log10(logit_df[,2])))), main = main)
  abline(h = -log10(0.05/dim(logit_df)[1]), col = "red")
  abline(h = -log10(0.05), col="navy")
  abline(v = seq(1,(dim(logit_df)[1])), lty = 3, col = "grey")
  axis(1, at = 1:(dim(logit_df)[1]), ifelse(logit_df[, 1] < 0, yes = gsub('[.0.0]', '', rownames(logit_df)),no = ""), las = 2, col.axis = MyPal[2], cex.axis=0.5)
  axis(1, at = 1:(dim(logit_df)[1]), ifelse(logit_df[, 1] < 0, yes = "", gsub('[.0.0]', '', rownames(logit_df))), las = 2, col.axis = MyPal[8], cex.axis=0.5)
  legend("topleft", xpd=TRUE, legend = c(paste("Negative", expression(beta)), paste("Positive",expression(beta))), pch = c(19, 19),col = c(MyPal[2], MyPal[8]), cex = 0.5)
  legend("topright", xpd=TRUE, legend = c("Bonferroni", "P=0.05"),lty = 1, lwd = 3, col = c("red","navy"), cex = 0.5)
  }
```

## Preparation for analysis: function for manhattan_plot(BH)(one subtype)
```{r}
manhattan_plot_BH = function(logit_df, main){
  MyPal = brewer.pal("Paired", n = 12)
  par(mar=c(7, 0.5, 2, 0.5))
  # plot(-log10(logit_df[, 2]), pch = 20, col = ifelse(logit_df[, 1] < 0, yes = MyPal[2], no = MyPal[8]), xaxt = "n", ylab = expression(-log[10](italic(p))), xlab = "", las = 1, ylim = c(min(c(-log10(logit_df[,2]))), sort(c(-log10(logit_df[,2])), decreasing = TRUE)[3]), main = main)
  plot(-log10(logit_df[, 3]), pch = 20, col = ifelse(logit_df[, 1] < 0, yes = MyPal[2], no = MyPal[8]), xaxt = "n", ylab = expression(-log[10](italic(p))), xlab = "", las = 1, ylim = c(min(c(-log10(logit_df[,3]))), max(c(-log10(logit_df[,3])))), main = main)
  # par(new= TRUE)
  # plot(-log10(logit_df[,3]), pch = 18,  col = "red", xlab = "", ylab = "", xaxt = "n")
  # abline(h = -log10(0.05/dim(logit_df)[1]), col = "red")
  abline(h = -log10(0.05), col="navy")
  abline(v = seq(1,(dim(logit_df)[1])), lty = 3, col = "grey")
  axis(1, at = 1:(dim(logit_df)[1]), ifelse(logit_df[, 1] < 0, yes = gsub('[.0.0]', '', rownames(logit_df)),no = ""), las = 2, col.axis = MyPal[2], cex.axis=0.5)
  axis(1, at = 1:(dim(logit_df)[1]), ifelse(logit_df[, 1] < 0, yes = "", gsub('[.0.0]', '', rownames(logit_df))), las = 2, col.axis = MyPal[8], cex.axis=0.5)
  legend("topleft", xpd=TRUE, legend = c(paste("Negative", expression(beta)), paste("Positive",expression(beta))), pch = c(19, 19),col = c(MyPal[2], MyPal[8]), cex = 0.5)
  # legend("topright", xpd=TRUE, legend = c("P=0.05"),lty = 1, lwd = 3, col = c("red","navy"), cex = 0.5)
  }
```

## Uni-variate analysis 
### Uni-variate analysis on femalecancer_incident_case
```{r}
ukb_female = ukb %>% select(-ovary_incident_case, -uterus_incident_case, -breast_incident_case)
# ukb_female = ukb %>% select(-ovary_incident_case, -uterus_incident_case, -others_incident_case, -breast_incident_case)
# Factor Outcome
ukb_female$femalecancer_incident_case = factor(ukb_female$femalecancer_incident_case)
```

```{r}
ukb_female_logit = uni_var_anly(ukb_female, ) 
ukb_female_logit = as.data.frame(ukb_female_logit)
ukb_female_logit = ukb_female_logit %>% mutate(P_val_BH = p.adjust(ukb_female_logit$`P value`, method="BH"))
```

### Uni-variate analysis on breast_incident_case
```{r}
ukb_breast = ukb %>% filter(uterus_incident_case == 0 | breast_incident_case==1) %>% 
  filter(ovary_incident_case == 0 | breast_incident_case==1) %>% 
  # filter(others_incident_case == 0| breast_incident_case==1) %>% 
  select(-ovary_incident_case, -uterus_incident_case,-femalecancer_incident_case) 
  # select(-ovary_incident_case, -uterus_incident_case, -others_incident_case,-femalecancer_incident_case) 

# Factor Outcome
ukb_breast$breast_incident_case = factor(ukb_breast$breast_incident_case)
```

```{r}
ukb_breast_logit = uni_var_anly(ukb_breast, ) 
ukb_breast_logit = as.data.frame(ukb_breast_logit)
ukb_breast_logit = ukb_breast_logit %>% mutate(P_val_BH = p.adjust(ukb_breast_logit$`P value`, method="BH"))
```

### Uni-variate analysis on ovary_incident_case
```{r}
ukb_ovary = ukb %>% 
  filter(uterus_incident_case == 0 | ovary_incident_case == 1 ) %>% 
  filter(breast_incident_case == 0 | ovary_incident_case == 1 ) %>% 
  # filter(others_incident_case == 0 | ovary_incident_case == 1 ) %>% 
  select(-breast_incident_case, -uterus_incident_case,-femalecancer_incident_case) 
  # select(-breast_incident_case, -uterus_incident_case, -others_incident_case,-femalecancer_incident_case)

# Factor Outcome
ukb_ovary$ovary_incident_case = factor(ukb_ovary$ovary_incident_case)
```

```{r}
ukb_ovary_logit = uni_var_anly(ukb_ovary, ) 
ukb_ovary_logit = as.data.frame(ukb_ovary_logit)
ukb_ovary_logit = ukb_ovary_logit %>% mutate(P_val_BH = p.adjust(ukb_ovary_logit$`P value`, method="BH")) 
```

### Uni-variate analysis on uterus_incident_case
```{r}
ukb_uterus = ukb %>% filter(breast_incident_case == 0 | uterus_incident_case==1) %>% 
  filter(ovary_incident_case == 0| uterus_incident_case==1) %>% 
  # filter(others_incident_case == 0| uterus_incident_case==1) %>% 
  select(-ovary_incident_case, -breast_incident_case,-femalecancer_incident_case)
  # select(-ovary_incident_case, -breast_incident_case, -others_incident_case,-femalecancer_incident_case)

# Factor Outcome
ukb_uterus$uterus_incident_case = factor(ukb_uterus$uterus_incident_case)
```

```{r}
ukb_uterus_logit = uni_var_anly(ukb_uterus, ) 
ukb_uterus_logit = as.data.frame(ukb_uterus_logit)
ukb_uterus_logit = ukb_uterus_logit %>% mutate(P_val_BH = p.adjust(ukb_uterus_logit$`P value`, method="BH"))
```

### Univariate analysis on others_incident_case
```{r}
# ukb_others = ukb %>% filter(breast_incident_case == 0 | others_incident_case ==1) %>% filter(ovary_incident_case == 0 | others_incident_case ==1) %>% filter(uterus_incident_case == 0| others_incident_case ==1) %>% select(-ovary_incident_case, -breast_incident_case, -uterus_incident_case, -femalecancer_incident_case)
# 
# # Factor Outcome
# ukb_others$others_incident_case = factor(ukb_others$others_incident_case)

```

```{r}
# ukb_others_logit = uni_var_anly(ukb_others, "", ) 
# ukb_others_logit = as.data.frame(ukb_others_logit)
# ukb_others_logit = ukb_others_logit %>% mutate(P_val_BH = p.adjust(ukb_others_logit$`P value`, method="BH")) %>% select(-c("2.5%",  "97.5%")) 
```

```{r}
ukb_univar = cbind(ukb_female_logit, ukb_breast_logit, ukb_uterus_logit, ukb_ovary_logit)
colnames(ukb_univar) = c("Female_Estimate", "Female_P_value", "Female_2.5%", "Female_97.5%", "Female_P_val_BH", 
                        "Breast_Estimate", "Breast_P_value", "Breast_2.5%", "Breast_97.5%", "Breast_P_val_BH", 
                        "Uterus_Estimate", "Uterus_P_value", "Uterus_2.5%", "Uterus_97.5%", "Uterus_P_val_BH", 
                        "Ovary_Estimate", "Ovary_P_value", "Ovary_2.5%", "Ovary_97.5%","Ovary_P_val_BH")

ukb_univar$var = rownames(ukb_univar)
ukb_univar = ukb_univar %>% mutate(group=c(rep("Demo", 5), rep("Female",8), rep("Environment", 2), rep("Lifestyle", 11), rep("Diet", 16),rep("PhyMeas", 3), rep("Biomarker",32)))
ukb_univar = ukb_univar %>% mutate(color = recode(group, "Demo"="black", "Female"="pink", "Environment"="mediumseagreen", "Lifestyle"="orange", "Diet"="blue", "PhyMeas"="gold", "Biomarker"="olivedrab"))
write.csv(ukb_univar, "ukb_univar.csv")
rm(ukb_female_logit, ukb_breast_logit, ukb_uterus_logit, ukb_ovary_logit)
```


# Plot 
## Pheatmap for uni-variate analysis:
### Plot Pheatmap with base R
```{r}
# ukb_univar_heatmap = ukb_univar %>% select(Female_P_val_BH, Breast_P_val_BH, Uterus_P_val_BH, Ovary_P_val_BH)
# ukb_univar_heatmap = ukb_univar_heatmap %>% filter(Female_P_val_BH<=0.05|Breast_P_val_BH<=0.05|Uterus_P_val_BH<=0.05|Ovary_P_val_BH<=0.05)
# colnames(ukb_univar_heatmap) = c("Female cancer", "Breast cancer", "Uterus cancer", "Ovary cancer") 
# ukb_univar_heatmap = ifelse(ukb_univar_heatmap>= -log10(0.05),1,0)
# ukb_univar_heatmap = -log10(ukb_univar_heatmap)
# pheatmap(t(ukb_univar_heatmap), cluster_rows = FALSE, cluster_cols = FALSE, fontsize_row = 6, fontsize_col = 6, main ="Univariate analysis(B-H adjusted)", color=c("grey","red"), legend_breaks = 0.5, legend_labels = c("P=0.05"))
```

### Plot pheatmap with ggplot2
Data preparation for pheatmap:
```{r}
ukb_univar_heatmap = ukb_univar %>% select(Female_P_val_BH, Breast_P_val_BH, Uterus_P_val_BH, Ovary_P_val_BH, group, color)
ukb_univar_heatmap = ukb_univar_heatmap %>% filter(Female_P_val_BH<=0.05|Breast_P_val_BH<=0.05|Uterus_P_val_BH<=0.05|Ovary_P_val_BH<=0.05)
colnames(ukb_univar_heatmap) = c("Female cancer", "Breast cancer", "Uterus cancer", "Ovary cancer", "group", "color") 
ukb_univar_heatmap$`Female cancer` = -log10(ukb_univar_heatmap$`Female cancer`)
ukb_univar_heatmap$`Breast cancer` = -log10(ukb_univar_heatmap$`Breast cancer`)
ukb_univar_heatmap$`Uterus cancer` = -log10(ukb_univar_heatmap$`Uterus cancer`)
ukb_univar_heatmap$`Ovary cancer` = -log10(ukb_univar_heatmap$`Ovary cancer`)
                                            
ukb_univar_heatmap$var = rownames(ukb_univar_heatmap)

ukb_univar_heatmap = ukb_univar_heatmap %>% pivot_longer(cols = -c("var","group","color"), values_to = "P_value", names_to = "subtype")

```

```{r}
ukb_univar_heatmap_est = ukb_univar  %>% 
  filter(Female_P_val_BH<=0.05|Breast_P_val_BH<=0.05|Uterus_P_val_BH<=0.05|Ovary_P_val_BH<=0.05) %>%
  select(Female_Estimate, Breast_Estimate, Uterus_Estimate, Ovary_Estimate)
colnames(ukb_univar_heatmap_est) = c("Female cancer", "Breast cancer", "Uterus cancer", "Ovary cancer")
ukb_univar_heatmap_est$var = rownames(ukb_univar_heatmap_est)
ukb_univar_heatmap_est = ukb_univar_heatmap_est %>% pivot_longer(cols = -var, values_to = "Estimate", names_to = "subtype")
```

```{r}
ukb_univar_heatmap = inner_join(ukb_univar_heatmap, ukb_univar_heatmap_est, by = c("var" = "var", "subtype" = "subtype"))
ukb_univar_heatmap$var = factor(ukb_univar_heatmap$var, levels=unique(ukb_univar_heatmap$var))
ukb_univar_heatmap$subtype = factor(ukb_univar_heatmap$subtype, levels = unique(ukb_univar_heatmap$subtype))
```

Plot heatmap with ggplot2(geom_tile)
```{r, fig.height = 6, fig.width = 8}
ggplot(ukb_univar_heatmap, aes(x = subtype, y = var, fill = P_value*sign(Estimate))) +
  geom_tile() +
  geom_text(aes(label = ifelse(P_value >= -log10(0.05), round(sign(Estimate)*P_value,2), "")), size=3, color = "navy")+
  scale_fill_gradient2(low = "#FFD699", mid="white" , high = "#9966CC") +
  theme_classic()+
  labs(x="", y="", title="FDR for uni-variate analysis", fill = "Sign(β)*-log(P)")+
  theme(axis.text.y = element_text(size = 8, hjust=1, vjust = 0.5, color = ukb_univar_heatmap$color[seq(1, length(ukb_univar_heatmap$color), 4)]), plot.title = element_text(hjust = 0.5) )

# rm(ukb_univar_heatmap_est, ukb_univar_heatmap)
```



## Manhattan plot
```{r}
# # Data preparation
# ukb_uterus_logit = ukb_uterus_logit %>% select(-c("2.5%",  "97.5%")) 
# ukb_ovary_logit = ukb_ovary_logit %>% select(-c("2.5%",  "97.5%")) 
# ukb_breast_logit = ukb_breast_logit %>% select(-c("2.5%",  "97.5%"))
# ukb_female_logit = ukb_female_logit %>% select(-c("2.5%",  "97.5%")) 

```

```{r}
# manhattan_plot_BF(ukb_breast_logit,"Breast cancer(bonferroni)")
# manhattan_plot_BH(ukb_breast_logit,"Breast cancer(BH adjusted)")
```

```{r}
# manhattan_plot_BF(ukb_ovary_logit,"Ovary cancer(bonferroni)")
# manhattan_plot_BH(ukb_ovary_logit,"Ovary cancer(BH adjusted)")
```

```{r}
# manhattan_plot_BF(ukb_uterus_logit,"Uterus cancer(bonferroni)")
# manhattan_plot_BH(ukb_uterus_logit,"Uterus cancer(BH adjusted)")
```

```{r}
# manhattan_plot_BF(ukb_female_logit,"Female cancer(bonferroni)")
# manhattan_plot_BH(ukb_female_logit,"Female cancer(BH adjusted)")
```

```{r}
# manhattan_plot_BF(ukb_others_logit,"Other female genital cancer")
# manhattan_plot_BH(ukb_others_logit,"Other female genital cancer(BH)")
```


### Plot primary analysis and subtype(breast cancer, ovary cancer, and uterus cancer) in ont plot
```{r}
# ## Pre-processing data
# cancer = cbind(ukb_female_logit[,3], ukb_breast_logit[,3], ukb_uterus_logit[,3], ukb_ovary_logit[,3])
# rownames(cancer) = rownames(ukb_breast_logit)
# colnames(cancer) = c("Female_cancer", "Breast_cancer", "Uterus_cancer", "Ovary_cancer")
# cancer = as.data.frame(cancer)
# cancer_plot = cancer %>% filter(Female_cancer < 0.05 | Breast_cancer< 0.05 | Uterus_cancer< 0.05 |Ovary_cancer< 0.05)
# 
# ## Plot Manhattan plot
# MyPal = brewer.pal("Paired", n = 12)
# y_lowerbound = min(-log10(cancer_plot))
# y_upperbound = max(-log10(cancer_plot))
# par(mar=c(9, 0.5, 2, 0.5))
# plot(-log10(cancer_plot[, 1]), pch = 18, col = MyPal[8], xaxt = "n", ylab = "", xlab = "", 
#      las = 1, ylim = c(y_lowerbound, y_upperbound))
# par(new= TRUE)
# plot(-log10(cancer_plot[, 2]), pch = 20, col = MyPal[3], xaxt = "n", ylab = "", xlab = "", 
#      las = 1, ylim = c(y_lowerbound, y_upperbound))
# par(new= TRUE)
# plot(-log10(cancer_plot[, 3]), pch = 20, col = MyPal[2], xaxt = "n", ylab = "", xlab = "", 
#      las = 1, ylim = c(y_lowerbound, y_upperbound))
# par(new= TRUE)
# plot(-log10(cancer_plot[, 4]), pch = 20, col = MyPal[5], xaxt = "n", ylab = expression(-log[10](italic(p))), xlab = "", 
#      las = 1, ylim = c(y_lowerbound, y_upperbound), main = "Manhattan plot")
# abline(h = -log10(0.05), col="navy")
# axis(1, at = 1:(dim(cancer_plot)[1]), rownames(cancer_plot), las = 2, col.axis = "navy", cex.axis=0.8)
# legend("topleft", xpd=TRUE, legend = c("Female", "Breast", "Uterus", "Ovary"), pch = c(18, 20, 20, 20), col = c(MyPal[8], MyPal[3], MyPal[2], MyPal[5]), cex = 0.6)

```

