---
title: "TDS_Female_Cancers_stability_selection" Constance

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Pre-analysis
```{r cars}
suppressPackageStartupMessages(library(glmnet))
suppressPackageStartupMessages(library(igraph))
suppressPackageStartupMessages(library(pheatmap))
suppressPackageStartupMessages(library(fake))
suppressPackageStartupMessages(library(sharp))
suppressPackageStartupMessages(library(tidyverse))
```

```{r}
# set up working directory
rm(list=ls())
path <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(path)

# load packages
#library(tidyverse)
library(dplyr)
library(RColorBrewer)
library(mice)
library(gglasso)
#library(devtools)
#install_github("barbarabodinier/sharp")
# install_github("barbarabodinier/fake")
library(OpenMx)
library(igraph)
library(sharp)
library(fake)
rm(path)

# Read in dataset 
ukb = readRDS("ukb_varsel_0501.rds")
```

## Transform factors to ordinal variables
```{r}
# Re-code Sleep_snoring.0.0 and Female_Ever_use_HRT.0.0 (binary variables)
ukb$Sleep_snoring.0.0 = ifelse(ukb$Sleep_snoring.0.0=="No", 0, 1)
ukb$Female_Ever_use_HRT.0.0 = ifelse(ukb$Female_Ever_use_HRT.0.0=="No", 0, 1)

# Select factor variables
ukb_cate= ukb %>% select(eid, is.factor)

# Transform factors into ordinal variables
ukb_ordinal = as.data.frame(lapply(ukb_cate, as.numeric))
  
# Select non factor variables
ukb_nonfactor = ukb %>% select(-is.factor)
ukb_nonfactor$eid = as.numeric(ukb$eid)

# Merge
ukb = inner_join(ukb_ordinal, ukb_nonfactor)

rm(ukb_cate, ukb_ordinal, ukb_nonfactor)
```

## factor binary variables(only for univariate analysis)
```{r}
## factor binary variables(only for univariate variables)
# ukb$Sleep_snoring.0.0 = factor(ukb$Sleep_snoring.0.0)
# ukb$Mother_breast_cancer = factor(ukb$Mother_breast_cancer)
# ukb$Mother_cancer = factor(ukb$Mother_cancer)
# ukb$Mother_breast_cancer = factor(ukb$Mother_breast_cancer)
# ukb$Mother_cancer = factor(ukb$Mother_cancer)
# ukb$Female_Menopause_no = factor(ukb$Female_Menopause_no )
# ukb$Female_Menopause_unsure = factor(ukb$Female_Menopause_unsure)
# ukb$Female_Menopause_yes = factor(ukb$Female_Menopause_yes)
# ukb$Female_Ever_use_HRT.0.0 = factor(ukb$Female_Ever_use_HRT.0.0)
# rm(ukb_cate, ukb_ordinal, ukb_nonfactor)
```

## Transform logical variables into numeric
```{r}
ukb$Mother_breast_cancer = as.numeric(ukb$Mother_breast_cancer)
```

## Pick up variables necessary for analysis and reorder the variables
```{r}
rownames(ukb) = ukb$eid
ukb = ukb %>% select(-eid)

# Re-arrange the  variables
## Biochemical metrics
sex_horm = c("Bio_shbg.0.0","Bio_testosterone.0.0")
glucose = c("Bio_glucose.0.0", "Bio_glycated_haemoglobin.0.0", "Bio_igf_1.0.0")
liver = c("Bio_alkaline_phosphate.0.0", "Bio_alanine_aminotransferase.0.0", "Bio_aspartate_aminotransferase.0.0", "Bio_direct_bilirubin.0.0", "Bio_gamma_glutamyltransferase.0.0", "Bio_total_bilirubin.0.0")
lipid = c("Bio_apolipoprotein_a.0.0", "Bio_apolipoprotein_b.0.0", "Bio_cholesterol.0.0", "Bio_hdl_cholesterol.0.0", "Bio_ldl_direct.0.0", "Bio_lipoprotein_a.0.0", "Bio_triglycerides.0.0")
nutrit = c("Bio_albumin.0.0", "Bio_total_protein.0.0")
inflam = c("Bio_c_reac_protein.0.0")
urate = c("Bio_urate.0.0")
skeleton = c("Bio_calcium.0.0", "Bio_phosphate.0.0", "Bio_vitamin_d.0.0")
kidney = c("Bio_urea.0.0", "Bio_creatinine.0.0", "Bio_cystatin_c.0.0")

## Physical Measurement, environment, and demographic variables
# PhyMeas = c("phyMeas_SBP", "phyMeas_DBP", "PhyMeas_waist_cir.0.0", "PhyMeas_BMI.0.0")
PhyMeas = c("PhyMeas_BMI.0.0", "phyMeas_SBP", "phyMeas_DBP")
demo = c("Age_enrollment.0.0", "income_household.0.0", "Education","Employment_no_or_cnt_wk","Employment_paid_or_sf_emply","Employment_unpaid_wk_or_funded")
PhyAC = c("Days_WK_PhyAc.0.0")
envir = c("no2_air_pol.0.0","no_air_pol.0.0")

ukb = ukb %>% select(
  all_of(demo), 
  starts_with("Female_"), 
  starts_with("Mother_"), 
  envir, 
  PhyAC,
  starts_with("Sleep_"), 
  starts_with("Smoke_"), 
  starts_with("Alcohol_"), 
  starts_with("Diet_"), 
  all_of(PhyMeas),
  all_of(sex_horm), 
  all_of(glucose), 
  all_of(liver), 
  all_of(lipid), 
  all_of(nutrit), 
  all_of(inflam), 
  all_of(urate), 
  all_of(skeleton), 
  all_of(kidney), 
  starts_with("Urine_"),
  breast_incident_case,
  uterus_incident_case, 
  ovary_incident_case, 
  # others_incident_case, 
  femalecancer_incident_case)

rm(PhyMeas, demo, envir, sex_horm, glucose, liver, lipid, nutrit, inflam, urate, skeleton, kidney)

```

Binary variabels
```{r}
# To decide whether scale binary variables or not: the following are binary variables 
# Binary_variable = c("Employment_no_or_cnt_wk", "Employment_paid_or_sf_emply", "Employment_unpaid_wk_or_funded", "Female_Ever_use_HRT.0.0", "Female_Menopause_no", "Female_Menopause_unsure", "Female_Menopause_yes", "Mother_breast_cancer")
```

Create data set for each cancer
```{r}
# Female cancer
ukb_female = ukb %>% select(-ovary_incident_case, -uterus_incident_case, -breast_incident_case)
# ukb_female = ukb %>% select(-ovary_incident_case, -uterus_incident_case, -others_incident_case, -breast_incident_case)

# Factor Outcome
ukb_female$femalecancer_incident_case = factor(ukb_female$femalecancer_incident_case)

# Split X and Y
ukb_female_x = as.matrix(ukb_female %>% select(-femalecancer_incident_case))
ukb_female_x = scale(ukb_female_x)
ukb_female_y = as.matrix(ukb_female %>% select(femalecancer_incident_case))
```

```{r}
# Breat cancer
# ukb_breast = ukb %>% filter(uterus_incident_case == 0 | breast_incident_case==1) %>% 
#   filter(ovary_incident_case == 0 | breast_incident_case==1) %>% 
#   filter(others_incident_case == 0| breast_incident_case==1) %>% 
#   select(-ovary_incident_case, -uterus_incident_case, -others_incident_case,-femalecancer_incident_case)
ukb_breast = ukb %>% filter(uterus_incident_case == 0 | breast_incident_case==1) %>% 
  filter(ovary_incident_case == 0 | breast_incident_case==1) %>% 
  select(-ovary_incident_case, -uterus_incident_case,-femalecancer_incident_case)

# Factor Outcome
ukb_breast$breast_incident_case = factor(ukb_breast$breast_incident_case)

# Split X and Y
ukb_breast_x = as.matrix(ukb_breast %>% select(-breast_incident_case))
ukb_breast_x = scale(ukb_breast_x)
ukb_breast_y = as.matrix(ukb_breast %>% select(breast_incident_case))

```

```{r}
# Ovary cancer
# ukb_ovary = ukb %>% filter(uterus_incident_case == 0 | ovary_incident_case == 1 ) %>%
#   filter(breast_incident_case == 0 | ovary_incident_case == 1 ) %>%
#   filter(others_incident_case == 0 | ovary_incident_case == 1 ) %>%
#   select(-breast_incident_case, -uterus_incident_case, -others_incident_case,-femalecancer_incident_case)
ukb_ovary = ukb %>% filter(uterus_incident_case == 0 | ovary_incident_case == 1 ) %>%
  filter(breast_incident_case == 0 | ovary_incident_case == 1 ) %>%
  select(-breast_incident_case, -uterus_incident_case,-femalecancer_incident_case)

# Factor Outcome
ukb_ovary$ovary_incident_case = factor(ukb_ovary$ovary_incident_case)

# Split X and Y
ukb_ovary_x = as.matrix(ukb_ovary %>% select(-ovary_incident_case))
ukb_ovary_x = scale(ukb_ovary_x)
ukb_ovary_y = as.matrix(ukb_ovary %>% select(ovary_incident_case))
```

```{r}
# Uterus cancer
# ukb_uterus = ukb %>% filter(breast_incident_case == 0 | uterus_incident_case==1) %>% filter(ovary_incident_case == 0| uterus_incident_case==1) %>% filter(others_incident_case == 0| uterus_incident_case==1) %>% select(-ovary_incident_case, -breast_incident_case, -others_incident_case,-femalecancer_incident_case)
ukb_uterus = ukb %>% filter(breast_incident_case == 0 | uterus_incident_case==1) %>% 
  filter(ovary_incident_case == 0| uterus_incident_case==1) %>% 
  select(-ovary_incident_case, -breast_incident_case,-femalecancer_incident_case)

# Factor Outcome
ukb_uterus$uterus_incident_case = factor(ukb_uterus$uterus_incident_case)

# Split X and Y
ukb_uterus_x = as.matrix(ukb_uterus %>% select(-uterus_incident_case))
ukb_uterus_x = scale(ukb_uterus_x)
ukb_uterus_y = as.matrix(ukb_uterus %>% select(uterus_incident_case))
```

# Stability selection LASSO
## Running Stability Selection on all risk factors(unadjusted)
```{r}
# varSel_female <- VariableSelection(ukb_female_x, ukb_female_y, family = "binomial") 
# varSel_breast = VariableSelection(ukb_breast_x, ukb_breast_y, family = "binomial")
# varSel_uterus = VariableSelection(ukb_uterus_x, ukb_uterus_y, family = "binomial")
# varSel_ovary = VariableSelection(ukb_ovary_x, ukb_ovary_y, family = "binomial")
```

## Running Stability Selection LASSO on Bio Urine metrics adjusted for Age
```{r}
# ukb_female_bio_x = as.data.frame(ukb_female_x) %>% select(c("Age_enrollment.0.0"), starts_with("Bio_"), starts_with("Urine"))
# ukb_breast_bio_x = as.data.frame(ukb_breast) %>% select(c("Age_enrollment.0.0"), starts_with("Bio_"), starts_with("Urine"))
# ukb_uterus_bio_x = as.data.frame(ukb_uterus) %>% select(c("Age_enrollment.0.0"), starts_with("Bio_"), starts_with("Urine"))
# ukb_ovary_bio_x = as.data.frame(ukb_ovary) %>% select(c("Age_enrollment.0.0"), starts_with("Bio_"), starts_with("Urine"))
# 
# 
# varSel_female_bio = VariableSelection(ukb_female_bio_x, ukb_female_y, family = "binomial", penalty.factor = c(rep(0, 1), rep(1, dim(ukb_female_bio_x)[2]-1)))
# varSel_breast_bio = VariableSelection(ukb_breast_bio_x, ukb_breast_y, family = "binomial", penalty.factor = c(rep(0, 1), rep(1, dim(ukb_breast_bio_x)[2]-1)))
# varSel_uterus_bio = VariableSelection(ukb_uterus_bio_x, ukb_uterus_y, family = "binomial", penalty.factor = c(rep(0, 1), rep(1, dim(ukb_uterus_bio_x)[2]-1)))
# varSel_ovary_bio = VariableSelection(ukb_ovary_bio_x, ukb_ovary_y, family = "binomial", penalty.factor = c(rep(0, 1), rep(1, dim(ukb_ovary_bio_x)[2]-1)))
# 
# 
# selprop_bio = cbind(SelectionProportions(varSel_female_bio),
#                     SelectionProportions(varSel_breast_bio), 
#                     SelectionProportions(varSel_uterus_bio), 
#                     SelectionProportions(varSel_ovary_bio))
# rm(ukb_female_bio_x, ukb_breast_bio_x, ukb_uterus_bio_x, ukb_ovary_bio_x)
```

## Running Stability Selection LASSO on Environment factors adjusted for Age
```{r}
# ukb_female_env_x = as.data.frame(ukb_female_x) %>% select(-starts_with("Bio_"), -starts_with("Urine"))
# ukb_breast_env_x = as.data.frame(ukb_breast) %>% select(-starts_with("Bio_"), -starts_with("Urine"))
# ukb_uterus_env_x = as.data.frame(ukb_uterus) %>% select(-starts_with("Bio_"), -starts_with("Urine"))
# ukb_ovary_env_x = as.data.frame(ukb_ovary) %>% select(-starts_with("Bio_"), -starts_with("Urine"))
# 
# 
# varSel_female_env = VariableSelection(ukb_female_env_x, ukb_female_y, family = "binomial", penalty.factor = c(rep(0, 1), rep(1, dim(ukb_female_env_x)[2]-1)))
# varSel_breast_env = VariableSelection(ukb_breast_env_x, ukb_breast_y, family = "binomial", penalty.factor = c(rep(0, 1), rep(1, dim(ukb_breast_env_x)[2]-1)))
# varSel_uterus_env = VariableSelection(ukb_uterus_env_x , ukb_uterus_y, family = "binomial", penalty.factor = c(rep(0, 1), rep(1, dim(ukb_uterus_env_x)[2]-1)))
# varSel_ovary_env = VariableSelection(ukb_ovary_env_x, ukb_ovary_y, family = "binomial", penalty.factor = c(rep(0, 1), rep(1, dim(ukb_ovary_env_x)[2]-1)))
# 
# selprop_env = cbind(varSel_female_env, varSel_breast_env, varSel_uterus_env, varSel_ovary_env)
# rm(ukb_female_env_x, ukb_breast_env_x, ukb_uterus_env_x, ukb_ovary_env_x)
# rm(varSel_female_env, varSel_breast_env, varSel_uterus_env, varSel_ovary_env)

```

## Running Stability Selection LASSO on all risk factors adjusted for Age
```{r}
varSel_female = VariableSelection(ukb_female_x, ukb_female_y, family = "binomial", penalty.factor = c(rep(0, 1), rep(1, dim(ukb_female_x)[2]-1))) 
varSel_breast = VariableSelection(ukb_breast_x, ukb_breast_y, family = "binomial", penalty.factor = c(rep(0, 1), rep(1, dim(ukb_breast_x)[2]-1)))
varSel_uterus = VariableSelection(ukb_uterus_x, ukb_uterus_y, family = "binomial", penalty.factor = c(rep(0, 1), rep(1, dim(ukb_uterus_x)[2]-1)))
varSel_ovary = VariableSelection(ukb_ovary_x, ukb_ovary_y, family = "binomial", penalty.factor = c(rep(0, 1), rep(1, dim(ukb_ovary_x)[2]-1)))
```

# Visualization
## Calibration Plot
Stability score is color codes
```{r}
pdf("Calibration PLot(Stability selection lasso).pdf ")
par(mfrow=c(2,2), mar=c(2,2,2,2))
CalibrationPlot(varSel_female, cex.axis=0.5)
CalibrationPlot(varSel_breast, cex.axis=0.5)
CalibrationPlot(varSel_uterus, cex.axis=0.5)
CalibrationPlot(varSel_ovary, cex.axis=0.5)
dev.off()
```

## Calibrated selection proportions
```{r}
# Selection proportion
selprop_female <- SelectionProportions(varSel_female) 
selprop_breast <- SelectionProportions(varSel_breast) 
selprop_uterus <- SelectionProportions(varSel_uterus) 
selprop_ovary <- SelectionProportions(varSel_ovary)

selprop = cbind(selprop_female, selprop_breast, selprop_uterus, selprop_ovary)
selprop = as.data.frame(selprop)
```

```{r}
# Stability selection threshold
smry_stab_lasso = as.data.frame(rbind(Argmax(varSel_female), Argmax(varSel_breast), Argmax(varSel_uterus), Argmax(varSel_ovary)))
rownames(smry_stab_lasso) = c("female cancer", "breast cancer", "uterus cancer", "ovary cancer")
write.csv(smry_stab_lasso, "smry_stab_lasso.csv")
```

## Refit with stably selected variable
Refit
```{r}
varSel_female_refit=Refit(ukb_female_x, ukb_female_y, family = "binomial", stability = varSel_female)
varSel_breast_refit=Refit(ukb_breast_x, ukb_breast_y, family = "binomial", stability = varSel_breast)
varSel_uterus_refit=Refit(ukb_uterus_x, ukb_uterus_y, family = "binomial", stability = varSel_uterus)
varSel_ovary_refit=Refit(ukb_ovary_x, ukb_ovary_y, family = "binomial", stability = varSel_ovary)

rm(ukb_female_x, ukb_female_y, ukb_female, ukb_breast_x, ukb_breast_y, ukb_breast, ukb_ovary_x, ukb_ovary_y, ukb_ovary, ukb_uterus_x, ukb_uterus_y, ukb_uterus, ukb)
```
Result of refit 
```{r}
varSel_female_coef = as.data.frame(varSel_female_refit$coefficients[-1])
colnames(varSel_female_coef) = "coef_female"
varSel_female_coef$var = rownames(varSel_female_coef)

varSel_breast_coef = as.data.frame(varSel_breast_refit$coefficients[-1])
colnames(varSel_breast_coef) = "coef_breast"
varSel_breast_coef$var = rownames(varSel_breast_coef)

varSel_uterus_coef = as.data.frame(varSel_uterus_refit$coefficients[-1])
colnames(varSel_uterus_coef) = "coef_uterus"
varSel_uterus_coef$var = rownames(varSel_uterus_coef)

varSel_ovary_coef = as.data.frame(varSel_ovary_refit$coefficients[-1])
colnames(varSel_ovary_coef) = "coef_ovary"
varSel_ovary_coef$var = rownames(varSel_ovary_coef)
rm(varSel_female_refit, varSel_breast_refit, varSel_uterus_refit, varSel_ovary_refit)
```


## Effect size of variables passing stability selection 
```{r}
# Merge selection proportion and effect size
selprop$var = rownames(selprop)
selprop = left_join(selprop, varSel_female_coef, by=c("var"="var"))
selprop = left_join(selprop, varSel_breast_coef, by=c("var"="var"))
selprop = left_join(selprop, varSel_uterus_coef, by=c("var"="var"))
selprop = left_join(selprop, varSel_ovary_coef, by=c("var"="var"))
rownames(selprop)=selprop$var
selprop = selprop %>% select(-var)
rm(varSel_female_coef, varSel_breast_coef, varSel_uterus_coef, varSel_ovary_coef)


# Renames rownames
rownames(selprop) = sub(".0.0", "", rownames(selprop))
rownames(selprop) = gsub("_", " ", rownames(selprop))

```


## Labels variables passing stability selection (Data preparation for plot)
```{r}
## Create labels column only for selected variables
selprop = selprop %>% mutate(var = rownames(selprop))
selprop = selprop %>% mutate(label_female=ifelse(selprop_female >= smry_stab_lasso[1,2],var, ""))
selprop = selprop %>% mutate(label_breast=ifelse(selprop_breast >= smry_stab_lasso[2,2],var, ""))
selprop = selprop %>% mutate(label_uterus=ifelse(selprop_uterus >= smry_stab_lasso[3,2],var, ""))
selprop = selprop %>% mutate(label_ovary=ifelse(selprop_ovary >= smry_stab_lasso[4,2], var, ""))
selprop = selprop %>% mutate(label_breast_ovary = ifelse(selprop_breast >= smry_stab_lasso[2,2]|selprop_ovary >= smry_stab_lasso[4,2], var, ""))
selprop = selprop %>% mutate(label_breast_uterus = ifelse(selprop_breast >= smry_stab_lasso[2,2]|selprop_uterus >= smry_stab_lasso[3,2], var, ""))
selprop = selprop %>% mutate(label_uterus_ovary = ifelse(selprop_uterus >= smry_stab_lasso[3,2]|selprop_ovary >= smry_stab_lasso[4,2], var, ""))
selprop$var = factor(selprop$var, levels=selprop$var)

# Add group label
selprop = selprop %>% mutate(group=c(rep("Demo", 5), rep("Female",8), rep("Environment", 2), rep("Lifestyle", 11), rep("Diet", 16),rep("PhyMeas", 3), rep("Biomarker",32)))

## Create color groups based on variable groups
selprop = selprop %>% mutate(color = recode(selprop$group, "Demo"="black", "Female"="pink", "Environment"="mediumseagreen", "Lifestyle"="orange", "Diet"="blue", "PhyMeas"="gold", "Biomarker"="olivedrab"))
```



```{r}
# Write
write.csv(selprop, "selprop.csv")
```


## Selection plot
### Plot selection plot
```{r, fig.width=10}
# Female cancer
par(mar=c(7,1,1,1))
ggplot(data=selprop, aes(x=var, y=selprop_female)) + 
  geom_col(width = 0.5, fill= ifelse(selprop$selprop_female>=smry_stab_lasso[1,2], "red", "grey")) + 
  theme_classic()+
  theme(axis.text.x.bottom = element_text(angle=45, size = 8, hjust=1, vjust = 1, color = selprop$color), plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = smry_stab_lasso[1,2], col = "red", linetype=2)+
  labs(title="Stability selection(female cancer)", y="selection proportion")

# Breast cancer
par(mar=c(7,1,1,1))
ggplot(data=selprop, aes(x=var, y=selprop_breast)) + 
  geom_col(width = 0.5, fill= ifelse(selprop$selprop_breast>=smry_stab_lasso[2,2], "red", "grey")) + 
  theme_classic()+
  theme(axis.text.x.bottom = element_text(angle=45, size = 8, hjust=1, vjust = 1, color = selprop$color),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = smry_stab_lasso[2,2], col = "red", linetype=2)+
  labs(title="Stability selection(breast cancer)", y="selection proportion")

# Uterus cancer
par(mar=c(7,1,1,1))
ggplot(data=selprop, aes(x=var, y=selprop_uterus)) + 
  geom_col(width = 0.5, fill= ifelse(selprop$selprop_uterus>=smry_stab_lasso[3,2], "red", "grey")) + 
  theme_classic()+
  theme(axis.text.x.bottom = element_text(angle=45, size = 8, hjust=1, vjust = 1, color = selprop$color),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = smry_stab_lasso[3,2], col = "red", linetype=2)+
  labs(title="Stability selection(Uterus cancer)", y="selection proportion")

# Ovary cancer
par(mar=c(7,1,1,1))
ggplot(data=selprop, aes(x=var, y=selprop_ovary)) + 
  geom_col(width = 0.5, fill= ifelse(selprop$selprop_ovary>=smry_stab_lasso[4,2], "red", "grey")) + 
  theme_classic()+
  theme(axis.text.x.bottom = element_text(angle=45, size = 8, hjust=1, vjust = 1, color = selprop$color),
        plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept = smry_stab_lasso[4,2], col = "red", linetype=2)+
  labs(title="Stability selection(Ovary cancer)", y="selection proportion")

```

## Plot for comparistion between different cancers 
```{r}
library(ggrepel)
## Breast cancer vs Ovary cancer
par(mar=c(2,6,2,6))
ggplot(data = selprop) + 
  geom_point(aes(y=selprop_ovary,x=selprop_breast, color = group)) + 
  geom_text_repel(aes(y=selprop_ovary,x=selprop_breast,label=label_breast_ovary), size=3)+
  theme_bw() + 
  labs(x="Selection proportion(Breast cancer)", y="Selection proportion(Ovary cancer)", title="Stability selection Lasso(Breast cancer vs Ovary cancer)", color = NULL)+
  theme(plot.title=element_text(hjust=0.5))+
  geom_hline(yintercept = smry_stab_lasso[4,2], linetype=2)+
  geom_vline(xintercept = smry_stab_lasso[2,2], linetype=2)+
  scale_color_manual(values=c("Demo"="black", "Female"="pink", "Environment"="mediumseagreen", "Lifestyle"="orange", "Diet"="blue", "PhyMeas"="gold", "Biomarker"="olivedrab"))

par(mar=c(2,6,2,6))
ggplot(data = selprop) + 
  geom_point(aes(y=coef_ovary, x=coef_breast, color = group)) + 
  geom_text_repel(aes(y=coef_ovary, x=coef_breast, label=label_breast_ovary), size=3)+
  theme_bw() + 
  labs(x="Coefficient (Breast cancer)", y="Coefficient (Ovary cancer)", title="Coefficient (Breast cancer vs Ovary cancer)", color = NULL)+
  theme(plot.title=element_text(hjust=0.5))+
  geom_hline(yintercept = 0, linetype=2)+
  geom_vline(xintercept = 0, linetype=2)+
  geom_abline(slope = 1, linetype=3, color = "grey")+
  geom_abline(slope = -1, linetype=3, color = "grey")+
  scale_color_manual(values=c("Demo"="black", "Female"="pink", "Environment"="mediumseagreen", "Lifestyle"="orange", "Diet"="blue", "PhyMeas"="gold", "Biomarker"="olivedrab"))
  
```
```{r}
## Breast cancer vs Uterus cancer
par(mar=c(2,6,2,6))
ggplot(data = selprop) + 
  geom_point(aes(y=selprop_uterus,x=selprop_breast, color=group)) + 
  geom_text_repel(aes(y=selprop_uterus,x=selprop_breast,label=label_breast_uterus), size=3)+
  theme_bw() + 
  labs(x="Selection proportion(Breast cancer)", y="Selection proportion(Uterus cancer)", title="Stability selection Lasso(Breast cancer vs Uterus cancer)",color=NULL)+
  theme(plot.title=element_text(hjust=0.5))+
  geom_hline(yintercept = smry_stab_lasso[3,2], linetype=2)+
  geom_vline(xintercept = smry_stab_lasso[2,2], linetype=2)

par(mar=c(2,6,2,6))
ggplot(data = selprop) + 
  geom_point(aes(y=coef_uterus, x=coef_breast, color = group)) + 
  geom_text_repel(aes(y=coef_uterus, x=coef_breast, label=label_breast_uterus), size=3)+
  theme_bw() + 
  labs(x="Coefficient (Breast cancer)", y="Coefficient (Uterus cancer)", title="Coefficient (Breast cancer vs Uterus cancer)", color = NULL)+
  theme(plot.title=element_text(hjust=0.5))+
  geom_hline(yintercept = 0, linetype=2)+
  geom_vline(xintercept = 0, linetype=2)+
  geom_abline(slope = 1, linetype=3, color = "grey")+
  geom_abline(slope = -1, linetype=3, color = "grey")+
  scale_color_manual(values=c("Demo"="black", "Female"="pink", "Environment"="mediumseagreen", "Lifestyle"="orange", "Diet"="blue", "PhyMeas"="gold", "Biomarker"="olivedrab"))

```


```{r}
## Ovary cancer vs Uterus cancer
par(mar=c(2,6,2,6))
ggplot(data = selprop) + 
  geom_point(aes(y=selprop_uterus,x=selprop_ovary, color=group)) + 
  geom_text_repel(aes(y=selprop_uterus,x=selprop_ovary,label=label_uterus_ovary), size=3)+
  theme_bw() + 
  labs(x="Selection proportion(Ovary cancer)", y="Selection proportion(Uterus cancer)", title="Stability selection Lasso(Ovary cancer vs Uterus cancer)", color=NULL)+
  theme(plot.title=element_text(hjust=0.5))+
  geom_hline(yintercept = smry_stab_lasso[3,2], linetype=2)+
  geom_vline(xintercept = smry_stab_lasso[4,2], linetype=2)

par(mar=c(2,6,2,6))
ggplot(data = selprop) + 
  geom_point(aes(y=coef_uterus, x=coef_ovary, color = group)) + 
  geom_text_repel(aes(y=coef_uterus, x=coef_ovary, label=label_uterus_ovary), size=3)+
  theme_bw() + 
  labs(x="Coefficient (Ovary cancer)", y="Coefficient (Uterus cancer)", title="Coefficient (Ovary cancer vs Uterus cancer)", color = NULL)+
  theme(plot.title=element_text(hjust=0.5))+
  geom_hline(yintercept = 0, linetype=2)+
  geom_vline(xintercept = 0, linetype=2)+
  geom_abline(slope = 1, linetype=3, color = "grey")+
  geom_abline(slope = -1, linetype=3, color = "grey")+
  scale_color_manual(values=c("Demo"="black", "Female"="pink", "Environment"="mediumseagreen", "Lifestyle"="orange", "Diet"="blue", "PhyMeas"="gold", "Biomarker"="olivedrab"))

```


## Heatmap with ggplot
Data preparation
Labels
```{r}
selprop_heatmap_label = selprop[,1:4]
selprop_heatmap_label$selprop_female = ifelse(selprop_heatmap_label$selprop_female >= Argmax(varSel_female)[2], 1, 0)
selprop_heatmap_label$selprop_breast = ifelse(selprop_heatmap_label$selprop_breast >= Argmax(varSel_breast)[2], 1, 0)
selprop_heatmap_label$selprop_uterus = ifelse(selprop_heatmap_label$selprop_uterus >= Argmax(varSel_uterus)[2], 1, 0)
selprop_heatmap_label$selprop_ovary = ifelse(selprop_heatmap_label$selprop_ovary >= Argmax(varSel_ovary)[2], 1, 0)
selprop_heatmap_label = selprop_heatmap_label %>% filter(selprop_female!=0|selprop_breast!=0|selprop_uterus!=0|selprop_ovary!=0)
colnames(selprop_heatmap_label) = c("Female", "Breast", "Uterus", "Ovary")

selprop_heatmap_label  = selprop_heatmap_label  %>% pivot_longer(cols = colnames(selprop_heatmap_label),names_to = "subtype", values_to = "label")
```

Estimate(Refit)
```{r}
selprop_heatmap_est = selprop %>% filter(selprop_female >= Argmax(varSel_female)[2]|
                                           selprop_breast >=Argmax(varSel_breast)[2]|
                                           selprop_uterus >= Argmax(varSel_uterus)[2]|
                                           selprop_ovary >= Argmax(varSel_ovary)[2])
selprop_heatmap_est = selprop_heatmap_est[,5:8]
colnames(selprop_heatmap_est) = c("Female", "Breast", "Uterus", "Ovary")
selprop_heatmap_est = selprop_heatmap_est  %>% pivot_longer(cols = colnames(selprop_heatmap_est),names_to = "subtype", values_to = "est")
```

Merge data: label, estimate, selection proportion
```{r}
selprop_heatmap = selprop[,c("selprop_female", "selprop_breast", "selprop_uterus", "selprop_ovary", "group","color")]
colnames(selprop_heatmap ) = c("Female", "Breast", "Uterus", "Ovary","group","color")
selprop_heatmap$var = rownames(selprop_heatmap)
selprop_heatmap = selprop_heatmap %>% filter(Female >= Argmax(varSel_female)[2]|
                                               Breast >= Argmax(varSel_breast)[2]|
                                               Uterus >= Argmax(varSel_uterus)[2]|
                                               Ovary >= Argmax(varSel_ovary)[2])

selprop_heatmap = selprop_heatmap %>% pivot_longer(cols = -c("group","var","color"), names_to = "subtype", values_to = "selprop")
selprop_heatmap = cbind(selprop_heatmap, selprop_heatmap_label[,2])
selprop_heatmap = cbind(selprop_heatmap, selprop_heatmap_est[,2])
selprop_heatmap$var = factor(selprop_heatmap$var, levels = unique(selprop_heatmap$var))
selprop_heatmap$subtype = factor(selprop_heatmap$subtype, levels = unique(selprop_heatmap$subtype))
# selprop_heatmap = selprop_heatmap %>% mutate(color = recode(selprop_heatmap$Group, "Demo"="black", "Female"="pink", "Environment"="mediumseagreen", "Lifestyle"="orange", "Diet"="blue", "PhyMeas"="gold", "Biomarker"="olivedrab"))
```

Plot heatmap
```{r}
ggplot(selprop_heatmap, aes(x = subtype, y = var, fill = selprop)) +
  geom_tile() +
  geom_text(aes(label = ifelse(label==1, selprop, "")), size=3, color = "navy")+
  scale_fill_gradient2(low = "white", high = "red") +
  theme_classic()+
  labs(x="", y="", title="Selection proportion by stability selection lasso", fill = "Sele Prop")+
  theme(axis.text.y = element_text(size = 8, hjust=1, vjust = 0.5, color = selprop_heatmap$color[seq(1, length(selprop_heatmap$color), 4)]), plot.title = element_text(hjust = 0.5))

ggplot(selprop_heatmap, aes(x = subtype, y = var, fill = est)) +
  geom_tile() +
  geom_text(aes(label = ifelse(label==1, round(est,2), "")), size=3, color = "navy")+
  scale_fill_gradient2(low = "blue", mid ="white", high = "red") +
  theme_classic()+
  labs(x="", y="", title="Effect size of stably selected variables", fill = "Effect size")+
  theme(axis.text.y = element_text(size = 8, hjust=1, vjust = 0.5, color = selprop_heatmap$color[seq(1, length(selprop_heatmap$color), 4)]), plot.title = element_text(hjust = 0.5))

rm(selprop_heatmap_label, selprop_heatmap_est, selprop_heatmap)
```






















